\documentclass[10pt,fleqn]{article}
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\usepackage[margin=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\begin{center}
\LARGE
Acknowledgements
\normalsize
\end{center}

The Carp Celtic Jam inherited the original book from the Ottawa Celtic Slow Jam, which was founded in 1996 and is still active today.  See http://www.siegelproductions.ca/slowjam/ for additional background.  We are grateful for and continue to benefit from the updates the OCSJ makes to the volumes of the their tune book.

The Carp Celtic Jam Tune Book consists of:
\begin{itemize}
\item adapted version of Volume I of the Ottawa Celtic Slow Jam Tune Book (pages 1-51)
\item adapted version of Volume II of the Ottawa Celtic Slow Jam Tune Book (pages 52-71)
\item adapted version of Volume III of the Ottawa Celtic Slow Jam Tune Book (pages 73-99)
\item Carp Celtic Jam Addendum (pages 100-224)
\item Carp Celtic Jam Addendum II (pages 225-)
\end{itemize}

The Carp Celtic Jam adaptations of the Ottawa Celtic Slow Jam volumes differ in only minor editorial ways.  For example, the names of several tunes have changed slightly, so that the same tune appears under one name in the index.

The intention of Carp Celtic Jam adaptations is to remain true to the original tune book, but to integrate nicely within the larger complete Carp Celtic Jam tune book.  It is intended that players can use the Carp Celtic Jam tune book at either the Carp Celtic Jam or the Ottawa Celtic Slow Jam.

Although this tune book evolves over time, a jam session will contain players who have printed or downloaded this tunebook at different times.  To avoid confusion at sessions, with rare exceptions, the page number for a given tune does not change between versions of the tune book.

\begin{flushright}
\setlength{\parskip}{0pt}
Robin Park,

maintainer of this tune book,

June 2019.
\end{flushright}
\end{document}

